---
title: "Disseminate Deep Learning Comparison Results"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
engine: knitr
editor_options: 
  chunk_output_type: inline
---

# Disseminate Deep Learning Comparison Results

Execute this script to create the figures and table data for publication.

## Setup

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(viridis)
library(tibble)
```

Define environment variables for AWS credentials and region, if not yet defined.

```{r}
# Sys.setenv(AWS_ACCESS_KEY_ID="")
# Sys.setenv(AWS_SECRET_ACCESS_KEY="")
# Sys.setenv(AWS_DEFAULT_REGION = "eu-west-1")
```

## Download and format study results

Define the AWS S3 connection details and the folder to download the Strategus outputs to.

```{r}
bucket <- "s3://ohdsi-dlc/"
region <- "eu-west-1"
s3Folder <- "dlc-output"
s3FolderValidation <- "dlc-output-validation"
s3FolderTable1 <- "dlc-output-table1"

saveFolder <- "~/Desktop/ohdsi-dlc-download"
saveFolderValidation <- "~/Desktop/ohdsi-dlc-download-validation"
saveFolderTable1 <- "~/Desktop/ohdsi-dlc-download-table1"
```

Download Strategus outputs from the development and validation steps.

```{r}
source("DownloadStrategusOutputFromS3.R")
s3Settings <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3Folder, bucket=bucket, region=region)
getModelsFromS3(s3Settings, saveFolder)

s3SettingsValidation <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3FolderValidation, bucket=bucket, region=region)
getModelsFromS3(s3SettingsValidation, saveFolderValidation)

s3SettingsTable1 <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3FolderTable1, bucket=bucket, region=region)
getModelsFromS3(s3SettingsTable1, saveFolderTable1)

```

Format Strategus output from the development step.

```{r}
source("FormatDevelopmentStrategusOutput.R")
strategusDevOutput <- getAllAuc(saveFolder)
```

Format Strategus output from the validation step.

```{r}
source("FormatValidationStrategusOutput.R")
strategusValOutput <- getAllAucValidation(saveFolderValidation)
```

Prepare heat map data.

```{r}
df <- dplyr::bind_rows(strategusDevOutput, strategusValOutput)

df <- df %>%
  mutate(cohort_definition_id = case_when(
    cohort_definition_id %in% c(298) ~ "Lung cancer",
    cohort_definition_id %in% c(10461) ~ "Bipolar disorder",
    cohort_definition_id %in% c(6243) ~ "Dementia",
    TRUE ~ "Data Error"
  )) %>%
  mutate(model_type = case_when(
    model_type %in% c("fitXgboost") ~ "Xgboost",
    model_type %in% c("Xgboost") ~ "Xgboost",
    model_type %in% c("logistic") ~ "Logistic regression",
    model_type %in% c("ResNet") ~ "ResNet",
    model_type %in% c("Transformer") ~ "Transformer",
    TRUE ~ "Data Error"
  )) %>%
  mutate(database_meta_data_id = case_when(
    database_meta_data_id %in% c(-1410378758) ~ "OPEHR",
    database_meta_data_id %in% c(1463865175) ~ "OPSES",
    database_meta_data_id %in% c(-795494529) ~ "AUSOM",
    database_meta_data_id %in% c(2139891622) ~ "IPCI",
    database_meta_data_id %in% c(1484143096) ~ "STARR-OMOP",
    database_meta_data_id %in% c(528172452) ~ "CUIMC",
    database_meta_data_id %in% c(-1709821257) ~ "GERDA",
    database_meta_data_id %in% c(67505556) ~ "JMDC",
    database_meta_data_id %in% c(970917581) ~ "MDCD",
    database_meta_data_id %in% c(78786751) ~ "MDCR",
    database_meta_data_id %in% c(-247464127) ~ "CCAE",
    TRUE ~ "Data Error"
  )) %>%
  mutate(validation_database_meta_data_id = case_when(
    validation_database_meta_data_id %in% c(-1410378758) ~ "OPEHR",
    validation_database_meta_data_id %in% c(1463865175) ~ "OPSES",
    validation_database_meta_data_id %in% c(-795494529) ~ "AUSOM",
    validation_database_meta_data_id %in% c(2139891622) ~ "IPCI",
    validation_database_meta_data_id %in% c(1484143096) ~ "STARR-OMOP",
    validation_database_meta_data_id %in% c(528172452) ~ "CUIMC",
    validation_database_meta_data_id %in% c(-1709821257) ~ "GERDA",
    validation_database_meta_data_id %in% c(67505556) ~ "JMDC",
    validation_database_meta_data_id %in% c(970917581) ~ "MDCD",
    validation_database_meta_data_id %in% c(78786751) ~ "MDCR",
    validation_database_meta_data_id %in% c(-247464127) ~ "CCAE",
    TRUE ~ "Data Error"
  ))

all_combinations <- expand.grid(
  database_meta_data_id = unique(df$database_meta_data_id),
  cohort_definition_id = unique(df$cohort_definition_id),
  model_type = unique(df$model_type),
  validation_database_meta_data_id = unique(df$validation_database_meta_data_id)
)

complete_data <- merge(all_combinations, df, by = c("database_meta_data_id", "validation_database_meta_data_id","cohort_definition_id", "model_type"), all.x = TRUE)

```

## Plot Discrimination AUROC

```{r}
complete_data$value <- complete_data$AUROC

color_data <- complete_data %>%
  mutate(text_color = ifelse(value > 0.75 | value < 0.5, "black", "white"))

p <- ggplot(complete_data, aes(x = validation_database_meta_data_id, y = database_meta_data_id, fill = value)) +
  geom_tile(na.rm = FALSE) +
  geom_text(aes(label = ifelse(is.na(value), NA, sprintf("%.2f", value))), color = color_data$text_color,
            vjust = 0.5, hjust = 0.5, size = 3, na.rm = TRUE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # scale_fill_gradient(low = "white", high = "blue") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_viridis(name="AUROC", limits = c(0.5, 1.0), option = "D", na.value = "#F0F0F0") +
  labs(title = NULL,
       x = "Validation database", y = "Development database", fill = "AUROC") +
  coord_fixed(ratio = 1) +
  theme(legend.position = "bottom", legend.direction = "horizontal",
        legend.text = element_text(hjust = 0.5),  # Centering text within the legend keys
        legend.title = element_text(hjust = 0.5),  # Horizontal justification (centered)
        legend.key.width = grid::unit(2, "cm"),  # Adjust key width
        legend.key.height = grid::unit(0.3, "cm"),  # Adjust key height
        legend.spacing.x = grid::unit(1, "cm"),  # Adjust spacing between keys
        legend.box.margin = margin(6, 6, 6, 6)) +
  guides(fill = guide_colorbar(nrow = 1, byrow = TRUE, title.position = "top", label.position = "bottom")) +
  facet_grid(cohort_definition_id ~ model_type)

print(p)
ggsave("heatmap.png", plot = p, width = 14, height = 8, dpi = 300)

```

## Plot calibration Eavg

```{r}
complete_data$value <- complete_data$Eavg

color_data <- complete_data %>%
  mutate(text_color = ifelse(value < 0.1, "white", "black"))

p <- ggplot(complete_data, aes(x = validation_database_meta_data_id, y = database_meta_data_id, fill = value)) +
  geom_tile(na.rm = FALSE) +
  geom_text(aes(label = ifelse(is.na(value), NA, sprintf("%.2f", value))), color = color_data$text_color,
            vjust = 0.5, hjust = 0.5, size = 3, na.rm = TRUE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # scale_fill_gradient(low = "white", high = "blue") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_viridis(name="Eavg", limits = c(0.0, 0.08), option = "D", na.value = "#F0F0F0") +
  labs(title = NULL,
       x = "Validation database", y = "Development database", fill = expression(E[avg])) +
  coord_fixed(ratio = 1) +
  theme(legend.position = "bottom", legend.direction = "horizontal",
        legend.text = element_text(hjust = 0.5),  # Centering text within the legend keys
        legend.title = element_text(hjust = 0.5),  # Horizontal justification (centered)
        legend.key.width = grid::unit(2, "cm"),  # Adjust key width
        legend.key.height = grid::unit(0.3, "cm"),  # Adjust key height
        legend.spacing.x = grid::unit(1, "cm"),  # Adjust spacing between keys
        legend.box.margin = margin(6, 6, 6, 6)) +
  guides(fill = guide_colorbar(nrow = 1, byrow = TRUE, title.position = "top", label.position = "bottom")) +
  facet_grid(cohort_definition_id ~ model_type)

print(p)
ggsave("heatmap-eavg.png", plot = p, width = 14, height = 8, dpi = 300)
```

## Plot Calibration AUPRC

```{r}
complete_data$value <- complete_data$AUPRC

color_data <- complete_data %>%
  mutate(text_color = ifelse(value < 0.1, "white", "black"))

p <- ggplot(complete_data, aes(x = validation_database_meta_data_id, y = database_meta_data_id, fill = value)) +
  geom_tile(na.rm = FALSE) +
  geom_text(aes(label = ifelse(is.na(value), NA, sprintf("%.2f", value))), color = color_data$text_color,
            vjust = 0.5, hjust = 0.5, size = 3, na.rm = TRUE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # scale_fill_gradient(low = "white", high = "blue") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_viridis(name="AUPRC", limits = c(0.0, 0.5), option = "D", na.value = "#F0F0F0") +
  labs(title = NULL,
       x = "Validation database", y = "Development database", fill = "AUPRC") +
  coord_fixed(ratio = 1) +
  theme(legend.position = "bottom", legend.direction = "horizontal",
        legend.text = element_text(hjust = 0.5),  # Centering text within the legend keys
        legend.title = element_text(hjust = 0.5),  # Horizontal justification (centered)
        legend.key.width = grid::unit(2, "cm"),  # Adjust key width
        legend.key.height = grid::unit(0.3, "cm"),  # Adjust key height
        legend.spacing.x = grid::unit(1, "cm"),  # Adjust spacing between keys
        legend.box.margin = margin(6, 6, 6, 6)) +
  guides(fill = guide_colorbar(nrow = 1, byrow = TRUE, title.position = "top", label.position = "bottom")) +
  facet_grid(cohort_definition_id ~ model_type)

print(p)
ggsave("heatmap-auprc.png", plot = p, width = 14, height = 10, dpi = 300)
```

## Save Table 1

```{r}
library(dplyr)
library(plyr)
library(writexl)
library(fs)

process_data <- function(data, column_name) {
  data <- data %>%
    mutate(across(everything(), trimws)) %>%
    mutate(value = trimws(paste0(.[[2]], " (", .[[3]], ")"))) %>%
    select(key = 1, value) %>%
    slice(1:which(key == "Medication use")) %>%
    head(-1)
  data$value[data$value == "()"] <- ""
  colnames(data)[2] <- column_name
  return(data)
}

process_and_combine_data <- function(data_list, column_names) {
  processed_frames <- mapply(process_data, data_list, column_names, SIMPLIFY = FALSE)
  combined_data <- Reduce(function(x, y) full_join(x, y, by = "key"), processed_frames)
  return(combined_data)
}

folder_path <- fs::path(saveFolderTable1, "models")
file_paths <- list.files(path = folder_path, full.names = TRUE)
column_names <- sub("\\.rds$", "", basename(file_paths))

datasets <- lapply(file_paths, readRDS)
final_data <- process_and_combine_data(datasets, column_names)
specified_prefixes <- c("ausom", "columbia", "stanford", "ipci", "opehr", "opses")
all_columns <- colnames(final_data)
key_column <- "key"

specified_patterns <- paste0("^", specified_prefixes)
other_columns <- setdiff(all_columns, c(key_column, grep(paste(specified_patterns, collapse = "|"), all_columns, value = TRUE)))
ordered_columns <- c(key_column, grep(paste(specified_patterns, collapse = "|"), all_columns, value = TRUE), other_columns)

final_data <- final_data[, ordered_columns]
write_xlsx(final_data, "dlc-table1.xlsx")
```
