---
title: "Disseminate Deep Learning Comparison Results"
date: "`r format(Sys.Date(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
engine: knitr
editor_options: 
  chunk_output_type: inline
---

# Disseminate Deep Learning Comparison Results

Execute this script to create the figures and table data for publication.

## Setup

```{r}
library(ggplot2)
library(tidyr)
library(dplyr)
library(viridis)
library(purrr)
library(tibble)
library(fs)
library(tidyverse)
library(aws.s3)
```

Define environment variables for AWS credentials and region, if not yet defined.

```{r}
# Sys.setenv(AWS_ACCESS_KEY_ID="")
# Sys.setenv(AWS_SECRET_ACCESS_KEY="")
# Sys.setenv(AWS_DEFAULT_REGION = "eu-west-1")
```

## Download and format study results

Define the AWS S3 connection details and the folder to download the Strategus outputs to.

```{r}
bucket <- "s3://ohdsi-dlc/"
region <- "eu-west-1"
s3Folder <- "dlc-output"
s3FolderValidation <- "dlc-output-validation"
s3FolderTable1 <- "dlc-output-table1"
s3FolderLearningCurve <- "dlc-output-learningcurve"

saveFolder <- "~/Desktop/ohdsi-dlc-download"
saveFolderValidation <- "~/Desktop/ohdsi-dlc-download-validation"
saveFolderTable1 <- "~/Desktop/ohdsi-dlc-download-table1"
saveFolderLearningCurve <- "~/Desktop/ohdsi-dlc-download-learningcurve"
```

Download Strategus outputs from the development and validation steps.

```{r}
source("DownloadStrategusOutputFromS3.R")
s3Settings <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3Folder, bucket=bucket, region=region)
getModelsFromS3(s3Settings, saveFolder)

s3SettingsValidation <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3FolderValidation, bucket=bucket, region=region)
getModelsFromS3(s3SettingsValidation, saveFolderValidation)

s3SettingsTable1 <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3FolderTable1, bucket=bucket, region=region)
getModelsFromS3(s3SettingsTable1, saveFolderTable1)

s3SettingsLearningCurve <- tibble(modelZipLocation = character(), bucket = character(), region = character()) |>
  add_row(modelZipLocation=s3FolderLearningCurve, bucket=bucket, region=region)
getModelsFromS3(s3SettingsLearningCurve, saveFolderLearningCurve)
```

Format Strategus output from the development step.

```{r}
source("FormatDevelopmentStrategusOutput.R")
strategusDevOutput <- getAllAuc(saveFolder)
```

Format Strategus output from the validation step.

```{r}
source("FormatValidationStrategusOutput.R")
strategusValOutput <- getAllAucValidation(saveFolderValidation)
```

Prepare heat map data.

```{r}
df <- dplyr::bind_rows(strategusDevOutput, strategusValOutput)

df <- df %>%
  mutate(cohort_definition_id = case_when(
    cohort_definition_id %in% c(298) ~ "Lung cancer",
    cohort_definition_id %in% c(10461) ~ "Bipolar disorder",
    cohort_definition_id %in% c(6243) ~ "Dementia",
    TRUE ~ "Data Error"
  )) %>%
  mutate(model_type = case_when(
    model_type %in% c("fitXgboost") ~ "XGBoost",
    model_type %in% c("Xgboost") ~ "XGBoost",
    model_type %in% c("logistic") ~ "Logistic regression",
    model_type %in% c("ResNet") ~ "ResNet",
    model_type %in% c("Transformer") ~ "Transformer",
    TRUE ~ "Data Error"
  )) %>%
  mutate(database_meta_data_id = case_when(
    database_meta_data_id %in% c(-1410378758) ~ "OPEHR",
    database_meta_data_id %in% c(1463865175) ~ "OPSES",
    database_meta_data_id %in% c(-795494529) ~ "AUSOM",
    database_meta_data_id %in% c(2139891622) ~ "IPCI",
    database_meta_data_id %in% c(1484143096) ~ "STARR-OMOP",
    database_meta_data_id %in% c(528172452) ~ "CUIMC",
    database_meta_data_id %in% c(-1709821257) ~ "GERDA",
    database_meta_data_id %in% c(67505556) ~ "JMDC",
    database_meta_data_id %in% c(970917581) ~ "MDCD",
    database_meta_data_id %in% c(78786751) ~ "MDCR",
    database_meta_data_id %in% c(-247464127) ~ "CCAE",
    TRUE ~ "Data Error"
  )) %>%
  mutate(validation_database_meta_data_id = case_when(
    validation_database_meta_data_id %in% c(-1410378758) ~ "OPEHR",
    validation_database_meta_data_id %in% c(1463865175) ~ "OPSES",
    validation_database_meta_data_id %in% c(-795494529) ~ "AUSOM",
    validation_database_meta_data_id %in% c(2139891622) ~ "IPCI",
    validation_database_meta_data_id %in% c(1484143096) ~ "STARR-OMOP",
    validation_database_meta_data_id %in% c(528172452) ~ "CUIMC",
    validation_database_meta_data_id %in% c(-1709821257) ~ "GERDA",
    validation_database_meta_data_id %in% c(67505556) ~ "JMDC",
    validation_database_meta_data_id %in% c(970917581) ~ "MDCD",
    validation_database_meta_data_id %in% c(78786751) ~ "MDCR",
    validation_database_meta_data_id %in% c(-247464127) ~ "CCAE",
    TRUE ~ "Data Error"
  ))

  
all_combinations <- expand.grid(
  database_meta_data_id = unique(df$database_meta_data_id),
  cohort_definition_id = unique(df$cohort_definition_id),
  model_type = unique(df$model_type),
  validation_database_meta_data_id = unique(df$validation_database_meta_data_id)
)

levels(all_combinations$database_meta_data_id) <- levels(all_combinations$validation_database_meta_data_id)

complete_data <- merge(all_combinations, df, by = c("database_meta_data_id", "validation_database_meta_data_id","cohort_definition_id", "model_type"), all.x = TRUE)

```

## Plot Discrimination AUROC

```{r}
complete_data$value <- complete_data$AUROC

color_data <- complete_data %>%
  mutate(text_color = ifelse(value > 0.75 | value < 0.5, "black", "white"))

p <- ggplot(complete_data, aes(x = validation_database_meta_data_id, y = database_meta_data_id, fill = value)) +
  geom_tile(na.rm = FALSE) +
  geom_text(aes(label = ifelse(is.na(value), NA, sprintf("%.2f", value))), color = color_data$text_color,
            vjust = 0.5, hjust = 0.5, size = 3, na.rm = TRUE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # scale_fill_gradient(low = "white", high = "blue") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_viridis(name="AUROC", limits = c(0.5, 1.0), option = "D", na.value = "#F0F0F0") +
  labs(title = NULL,
       x = "Validation database", y = "Development database", fill = "AUROC") +
  coord_fixed(ratio = 1) +
  theme(legend.position = "bottom", legend.direction = "horizontal",
        legend.text = element_text(hjust = 0.5),  # Centering text within the legend keys
        legend.title = element_text(hjust = 0.5),  # Horizontal justification (centered)
        legend.key.width = grid::unit(2, "cm"),  # Adjust key width
        legend.key.height = grid::unit(0.3, "cm"),  # Adjust key height
        legend.spacing.x = grid::unit(1, "cm"),  # Adjust spacing between keys
        legend.box.margin = margin(6, 6, 6, 6)) +
  guides(fill = guide_colorbar(nrow = 1, byrow = TRUE, title.position = "top", label.position = "bottom")) +
  facet_grid(cohort_definition_id ~ model_type)

print(p)
ggsave("heatmap.png", plot = p, width = 14, height = 8, dpi = 300)

```

## Plot Calibration Eavg

```{r}
library(ggplot2)
library(dplyr)
library(viridis)

complete_data$value <- complete_data$Eavg

color_data <- complete_data %>%
  mutate(text_color = ifelse(value < 0.03, "white", "black"))

# Custom format function to remove leading zero in exponent
custom_format <- function(x) {
  formatted <- sprintf("%.0e", x)
  formatted <- sub("e([+-])0", "e\\1", formatted)
  formatted
}

p <- ggplot(complete_data, aes(x = validation_database_meta_data_id, y = database_meta_data_id, fill = value)) +
  geom_tile(na.rm = FALSE) +
  geom_text(aes(label = ifelse(is.na(value), NA, custom_format(value))), 
            color = color_data$text_color,
            vjust = 0.5, 
            hjust = 0.5, 
            size = 3, 
            na.rm = TRUE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # scale_fill_gradient(low = "white", high = "blue") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_viridis(name = expression(E[avg]), limits = c(0.0, 0.05), option = "C", na.value = "#F0F0F0") +
  labs(title = NULL,
       x = "Validation database", y = "Development database", fill = expression(E[avg])) +
  coord_fixed(ratio = 1) +
  theme(legend.position = "bottom", 
        legend.direction = "horizontal",
        legend.text = element_text(hjust = 0.5),  # Centering text within the legend keys
        legend.title = element_text(hjust = 0.5),  # Horizontal justification (centered)
        legend.key.width = grid::unit(2, "cm"),  # Adjust key width
        legend.key.height = grid::unit(0.3, "cm"),  # Adjust key height
        legend.spacing.x = grid::unit(1, "cm"),  # Adjust spacing between keys
        legend.box.margin = margin(6, 6, 6, 6)) +
  guides(fill = guide_colorbar(nrow = 1, byrow = TRUE, title.position = "top", label.position = "bottom")) +
  facet_grid(cohort_definition_id ~ model_type)

print(p)
ggsave("heatmap-eavg.png", plot = p, width = 14, height = 8, dpi = 300)
```

## Plot Precision AUPRC

```{r}
complete_data$value <- complete_data$AUPRC

color_data <- complete_data %>%
  mutate(text_color = ifelse(value < 0.1, "white", "black"))

p <- ggplot(complete_data, aes(x = validation_database_meta_data_id, y = database_meta_data_id, fill = value)) +
  geom_tile(na.rm = FALSE) +
  geom_text(aes(label = ifelse(is.na(value), NA, sprintf("%.2f", value))), color = color_data$text_color,
            vjust = 0.5, hjust = 0.5, size = 3, na.rm = TRUE) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  # scale_fill_gradient(low = "white", high = "blue") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0)) +
  scale_fill_viridis(name="AUPRC", limits = c(0.0, 0.5), option = "D", na.value = "#F0F0F0") +
  labs(title = NULL,
       x = "Validation database", y = "Development database", fill = "AUPRC") +
  coord_fixed(ratio = 1) +
  theme(legend.position = "bottom", legend.direction = "horizontal",
        legend.text = element_text(hjust = 0.5),  # Centering text within the legend keys
        legend.title = element_text(hjust = 0.5),  # Horizontal justification (centered)
        legend.key.width = grid::unit(2, "cm"),  # Adjust key width
        legend.key.height = grid::unit(0.3, "cm"),  # Adjust key height
        legend.spacing.x = grid::unit(1, "cm"),  # Adjust spacing between keys
        legend.box.margin = margin(6, 6, 6, 6)) +
  guides(fill = guide_colorbar(nrow = 1, byrow = TRUE, title.position = "top", label.position = "bottom")) +
  facet_grid(cohort_definition_id ~ model_type)

print(p)
ggsave("heatmap-auprc.png", plot = p, width = 14, height = 10, dpi = 300)
```

## Plot Critical Difference AUROC

```{r}

library(tidyverse)
library(PMCMRplus)  # For Nemenyi test
library(reshape2)
library(scmamp)
library(ggplot2)

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)
filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_all.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_all.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# internal

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(database_meta_data_id == validation_database_meta_data_id) %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_internal.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_internal.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# external

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(database_meta_data_id != validation_database_meta_data_id) %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_external.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_external.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# dementia

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(cohort_definition_id == "Dementia") %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_dementia.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_dementia.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# bipolar

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(cohort_definition_id == "Bipolar disorder") %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_bipolar.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_bipolar.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# lung cancer

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(cohort_definition_id == "Lung cancer") %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_lungcancer.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_lungcancer.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# large data

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(database_meta_data_id == "OPEHR" | validation_database_meta_data_id == "OPSES") %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_large.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_large.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()

# small data
filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(AUROC)) %>%
  filter(database_meta_data_id != "OPEHR" | validation_database_meta_data_id != "OPSES") %>%
  select(instance_id, model_type, AUROC) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = AUROC) %>%
  select(-instance_id)

friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_small.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05)
dev.off()

png("CD_small.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05)
dev.off()
```

## Plot Critical Difference Eavg

```{r}

library(tidyverse)
library(PMCMRplus)  # For Nemenyi test
library(reshape2)
library(scmamp)
library(ggplot2)

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)
filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_all.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_all.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# internal

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(database_meta_data_id == validation_database_meta_data_id) %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_internal.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_internal.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# external

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(database_meta_data_id != validation_database_meta_data_id) %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_external.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_external.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# dementia

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(cohort_definition_id == "Dementia") %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_dementia.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_dementia.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# bipolar

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(cohort_definition_id == "Bipolar disorder") %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_bipolar.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_bipolar.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# lung cancer

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(cohort_definition_id == "Lung cancer") %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_lungcancer.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_lungcancer.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# large data

filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(database_meta_data_id == "OPEHR" | validation_database_meta_data_id == "OPSES") %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_large.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_large.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

# small data
filtered_data <- complete_data
filtered_data <- filtered_data %>%
  unite("instance_id", database_meta_data_id, validation_database_meta_data_id, cohort_definition_id, remove = FALSE)

filtered_data <- filtered_data %>%
  filter(!is.na(Eavg)) %>%
  filter(database_meta_data_id != "OPEHR" | validation_database_meta_data_id != "OPSES") %>%
  select(instance_id, model_type, Eavg) %>%
  tidyr::pivot_wider(names_from = model_type, values_from = Eavg) %>%
  select(-instance_id)
friedman_test_result <- scmamp::friedmanTest(as.matrix(filtered_data))

postscript("CD_small.eps", width = 7, height = 5, paper = "special", horizontal = FALSE)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()

png("CD_small.png", width = 1920, height = 320, res = 300)
plotCD(filtered_data, alpha = 0.05, decreasing = FALSE)
dev.off()
```

## Save Table 1

```{r}
library(dplyr)
library(plyr)
library(writexl)
library(fs)

process_data <- function(data, column_name) {
  data <- data %>%
    mutate(across(everything(), trimws)) %>%
    mutate(value = trimws(paste0(.[[2]], " (", .[[3]], ")"))) %>%
    select(key = 1, value) %>%
    slice(1:which(key == "Medication use")) %>%
    head(-1)
  data$value[data$value == "()"] <- ""
  colnames(data)[2] <- column_name
  return(data)
}

process_and_combine_data <- function(data_list, column_names) {
  processed_frames <- mapply(process_data, data_list, column_names, SIMPLIFY = FALSE)
  combined_data <- Reduce(function(x, y) full_join(x, y, by = "key"), processed_frames)
  return(combined_data)
}

folder_path <- fs::path(saveFolderTable1, "models")
file_paths <- list.files(path = folder_path, full.names = TRUE)
column_names <- sub("\\.rds$", "", basename(file_paths))

datasets <- lapply(file_paths, readRDS)
final_data <- process_and_combine_data(datasets, column_names)
specified_prefixes <- c("ausom", "columbia", "stanford", "ipci", "opehr", "opses")
all_columns <- colnames(final_data)
key_column <- "key"

specified_patterns <- paste0("^", specified_prefixes)
other_columns <- setdiff(all_columns, c(key_column, grep(paste(specified_patterns, collapse = "|"), all_columns, value = TRUE)))
ordered_columns <- c(key_column, grep(paste(specified_patterns, collapse = "|"), all_columns, value = TRUE), other_columns)

final_data <- final_data[, ordered_columns]
write_xlsx(final_data, "dlc-table1.xlsx")
```

## Plot Learning Curves

```{r}
# Define the models and databases to search for
models <- c("ResNet", "Transformer", "fitXgboost", "logistic")
databases <- c("cdm_optum_extended_ses", "cdm_optum_ehr")

# Get a list of all RDS files in the directory
file_list <- fs::dir_ls(fs::path(saveFolderLearningCurve, "models"), glob = "*.rds")

# Function to find a matching substring from a list of candidates
find_match <- function(string, candidates) {
  for (candidate in candidates) {
    if (grepl(candidate, string, fixed = TRUE)) {
      return(candidate)
    }
  }
  return(NA)
}

# Function to extract the number following "_O"
extract_number <- function(string) {
  match <- regexpr("_O\\d+", string)
  if (match != -1) {
    return(as.numeric(sub("_O", "", regmatches(string, match))))
  }
  return(NA)
}

# Function to process each file
process_file <- function(file_path) {
  # Extract filename without the extension
  filename <- fs::path_file(file_path)
  filename_without_ext <- fs::path_ext_remove(filename)
  
  # Find the model and database from the filename
  model <- find_match(filename_without_ext, models)
  database <- find_match(filename_without_ext, databases)
  outcome <- extract_number(filename_without_ext)

  # If no match is found for model, database, or number, return NULL
  if (is.na(model) || is.na(database) || is.na(outcome)) {
    return(NULL)
  }
  
  # Read the RDS file
  data <- readRDS(as.character(file_path))
  
  # Add the model, database, and number as new columns
  data <- data %>%
    mutate(Model = model, database = database, outcome = outcome)
  
  return(data)
}

# Use purrr::map_df to process all files and row-bind the results
all_data <- file_list %>%
  map_df(~ process_file(.x), .id = "source")

# Print the first few rows of the combined data frame
print(head(all_data))

# Optionally, save the combined data frame to a file
# saveRDS(all_data, "combined_data.rds")

```

```{r}
learningCurve <- all_data

metric <- "AUROC"
plotTitle <- NULL
plotSubtitle = NULL
fileName <- NULL

tidyLearningCurve <- NULL
yAxisRange <- NULL
y <- NULL

learningCurve <- as.data.frame(learningCurve)

# create a data.frame with evalautionType, AUROC
tidyLearningCurve <- learningCurve %>% 
  dplyr::rename(
    Occurrences = "Train_outcomeCount", 
    Observations = "Train_populationSize" ) %>%
  dplyr::select("trainFraction", "Occurrences", "Observations", "Test_AUROC", "Train_AUROC", "Model", "database", "outcome")

exclude_columns <- c("Model", "database", "outcome")
# Loop through each column and convert to double if it's not in the exclude list
for (i in seq_along(tidyLearningCurve)) {
  column_name <- names(tidyLearningCurve)[i]
  if (!(column_name %in% exclude_columns)) {
    tidyLearningCurve[, i] <- as.double(as.character(tidyLearningCurve[, i]))
  }
}

tidyLearningCurve <- tidyLearningCurve %>%
  mutate(outcome = case_when(
    outcome %in% c(298) ~ "Lung cancer",
    outcome %in% c(10461) ~ "Bipolar disorder",
    outcome %in% c(6243) ~ "Dementia",
    TRUE ~ "Data Error"
  )) %>%
  mutate(database = case_when(
    database %in% c("cdm_optum_ehr") ~ "OPEHR",
    database %in% c("cdm_optum_extended_ses") ~ "OPSES",
    TRUE ~ "Data Error"
  ))
  
tidyLearningCurve <- tidyr::pivot_longer(
  data = as.data.frame(tidyLearningCurve),
  cols = colnames(as.data.frame(tidyLearningCurve))[!colnames(as.data.frame(tidyLearningCurve)) %in% c('trainFraction', 'Occurrences', 'Observations', "Model", 'database', "outcome")], 
  values_to = "value", 
  names_to = 'variable'
)

tidyLearningCurve$Dataset <- sapply(tidyLearningCurve$variable, function(x)strsplit(as.character(x), '_')[[1]][1])
tidyLearningCurve$outcome <- factor(tidyLearningCurve$outcome, levels = c("Lung cancer", "Dementia", "Bipolar disorder"))

# define plot properties
yAxisRange <- c(0.5, 1.0)
xAxisRange <- c(0.0, 10000)

abscissa <- "Occurrences"
abscissaLabel <- "Outcome count"

tidyLearningCurve <- tidyLearningCurve %>%
  dplyr::filter(Dataset == "Test")

plot <- tidyLearningCurve %>%
  ggplot(aes(x = .data[[abscissa]], y = value, col = Model)) + # Use model as color and Dataset as linetype
  geom_line() +
  coord_cartesian(ylim = yAxisRange, xlim = xAxisRange, expand = FALSE) +
  labs(title = plotTitle, subtitle = plotSubtitle, 
    x = abscissaLabel, y = metric) +
  theme_minimal() +
  facet_grid(outcome ~ database)
  # facet_grid(~ outcome, scales = "free_x") 

  
plot

ggplot2::ggsave("lc.png", plot, width = 8, height = 4, dpi = 300)

```
